---
title: "sim"
author: "Bethany"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

library(brms)
library(shinystan)
library(rstan)
library(coda)
library(ggplot2)
library(bayesplot)
library(tidyverse)
library(parallel)
library(loo)
library(bridgesampling)
library(MASS)

```


# Questions: 


# To Do:

* figure out what to pull from models and calculate
log likelihood 

performance criteria. 


# Models




```{r}
mmrem_model<- '
data {
  int<lower=1> n;  // number of observations
  real y[n];       // outcome
  int<lower=1> J;  // number of group level coefficients; parameters
  real x[n];
  matrix[n, 4] w;
  int group1[n];
  int group2[n];
  int group3[n];
  int group4[n];
}


parameters {
  real<lower=0> sigma_u2;
  real<lower=0> sigma_y;
  real popint;
  real popslope;
  vector[J] u2;
}


model {

  //popint ~ normal(0,10);
  //popslope ~ normal(0,10);
  
  //precision is 1/variance. variance - 10,000
  popint ~ normal(0,100);
  popslope ~ normal(0,100);

  for (j in 1:J){
    u2[j] ~ normal(0,sigma_u2);
  }


  sigma_u2 ~ uniform(0,100);
  sigma_y ~ uniform(0, 100);

  for (i in 1:n){
  y[i] ~ normal(popint + popslope*x[i] + w[i,1] * u2[group1[i]] + w[i,2] * u2[group2[i]] + w[i,3] * u2[group3[i]] + w[i,4] * u2[group4[i]], sigma_y);
  } 
}


generated quantities {
vector[n] log_lik;
for (i in 1:n) {
log_lik[i] = normal_lpdf(y[i]| popint + popslope*x[i] + w[i,1] * u2[group1[i]] + w[i,2] * u2[group2[i]] + w[i,3] * u2[group3[i]] + w[i,4] * u2[group4[i]], sigma_y); 
// loop to run model prior to running Loo. 
}
}


'

ccrem_model<- '
data {
int<lower=1> n;  // number of observations
real y[n]; // observations
int<lower=1> J; // number of group level coefficients; parameters
real x[n];
int group1[n];
int group2[n];
int group3[n];
int group4[n];
}


parameters {
vector<lower=0>[4] sigma_u2;
real<lower=0> sigma_y;
real popint;
real popslope;
matrix[J, 4] u2;
//vector[4] u2[J]; // use this if you are doing it the other way.
}

model {

popint ~ normal(0,100);
popslope ~ normal(0,100);
  
  
for (j in 1:J){
for (k in 1:4){
u2[j,k] ~ normal(0,sigma_u2[k]);
}
}

sigma_u2 ~ uniform(0,100);
sigma_y ~ uniform(0, 100);


for (i in 1:n){
y[i] ~ normal(popint + popslope*x[i] + u2[group1[i],1] + u2[group2[i],2] + u2[group3[i],3] + u2[group4[i],4], sigma_y);
}


}

generated quantities {
vector[n] log_lik;
for (i in 1:n) {
log_lik[i] = normal_lpdf(y[i]| popint + popslope*x[i] + u2[group1[i],1] + u2[group2[i],2] + u2[group3[i],3] + u2[group4[i],4], sigma_y); 
// loop to run model prior to running Loo. 
}
}
'

rccrem_model_new <- 
'data {
  int<lower=1> n; // number of observations
  int<lower=1> J; //the number of levels of each type of school
  real x[n];
  int group1[n];
  int group2[n];
  int group3[n];
  int group4[n];
  matrix[4, 4] W;
  real y[n];      // observations
  vector<lower=0>[4] zeros;
}

parameters {
  real popint;
  real popslope;
  real<lower=0> sigma_y;
  vector<lower=0>[4] xi_u2;
  matrix[J,4] B_raw;
  cov_matrix[4] Tau_B_raw; // Sigma -> Tau_B_raw 
}

transformed parameters {
  matrix[J, 4] u2;
  cov_matrix[4] Sigma_B_raw;
  
  for (j in 1:J){
        for (k in 1:4){
             u2[j,k] = xi_u2[k]*B_raw[j,k];
        }
    }
  Sigma_B_raw = inverse(Tau_B_raw);
}



model {
  popint ~ normal(0,100);
  popslope ~ normal(0,100);
  sigma_y ~  uniform(0, 100);
  
  for (k in 1:4){
    xi_u2[k] ~ uniform(0, 100);
  }
  
  for (j in 1:J){
    B_raw[j,1:4] ~ multi_normal(zeros, Tau_B_raw); //u2 -> B_raw
  }
  
  Tau_B_raw ~ wishart(5, W);

  for (i in 1:n){
    y[i] ~ normal(popint + popslope*x[i] + u2[group1[i],1] + u2[group2[i],2] + u2[group3[i],3] + u2[group4[i],4], sigma_y);
  }
  
}

generated quantities {
  
  vector<lower=0>[4] sigma_u2;
  real<lower=-1,upper=1> rho_12;
  real<lower=-1,upper=1> rho_13;
  real<lower=-1,upper=1> rho_14;
  real<lower=-1,upper=1> rho_23;
  real<lower=-1,upper=1> rho_24;
  real<lower=-1,upper=1> rho_34;
  vector[n] log_lik;
  
  for (k in 1:4){
    sigma_u2[k] = xi_u2[k]*sqrt(Sigma_B_raw[k,k]);
  } 
  rho_12 = Sigma_B_raw[1,2]/sqrt(Sigma_B_raw[1,1]*Sigma_B_raw[2,2]);
  rho_13 = Sigma_B_raw[1,3]/sqrt(Sigma_B_raw[1,1]*Sigma_B_raw[3,3]);
  rho_14 = Sigma_B_raw[1,4]/sqrt(Sigma_B_raw[1,1]*Sigma_B_raw[4,4]);
  rho_23 = Sigma_B_raw[2,3]/sqrt(Sigma_B_raw[2,2]*Sigma_B_raw[3,3]);
  rho_24 = Sigma_B_raw[2,4]/sqrt(Sigma_B_raw[2,2]*Sigma_B_raw[4,4]);
  rho_34 = Sigma_B_raw[3,4]/sqrt(Sigma_B_raw[3,3]*Sigma_B_raw[4,4]);
    for (i in 1:n) {
    log_lik[i] = normal_lpdf(y[i]|popint + u2[group1[i],1] + u2[group2[i],2] + u2[group3[i],3] + u2[group4[i],4] + popslope*x[i], sigma_y); 
  }
}
'

```



# Data

May need to change this depending on parameters specification. 
```{r}
UDF_sample <- function(mobility, J, rho, tau) {
  require(MASS)
  
  
  m <- 10
  mu.X_init <- 0
  sigma2.X_init <- 1
  mu.u2_init <- rep(0,4)
  sigma2_init <- 10
  beta_init <- c(100,10)
  n<-m*J
  
  #use rho and tau
  
  if(tau == "same" & rho== FALSE){
    sigma2.u2_init <- matrix(0, 4, 4)  # Overwrite the old matrix
    diag(sigma2.u2_init) <-c(rep(10, 4))
    
  }else if(tau == "different" & rho== FALSE){
    
    sigma2.u2_init <- matrix(0, 4, 4)  # Overwrite the old matrix
    diag(sigma2.u2_init) <- c(10, 12, 14, 16)
    
  
  }else if(tau == "same" & rho== TRUE){
    
    rho <- rbind(c(10,6,5,4),c(6,10,6,5),c(5,6,10,6),c(4,5,6,10))*.1
    tau1 <- c(rep(10, 4))
    sigma2.u2_init <- sqrt(tau1)%*%t(sqrt(tau1))*rho
    
    
  }else{
    
    rho <- rbind(c(10,6,5,4),c(6,10,6,5),c(5,6,10,6),c(4,5,6,10))*.1
    tau2 <- c(10, 12, 14, 16)
    
    sigma2.u2_init <- sqrt(tau2)%*%t(sqrt(tau2))*rho
    
  }
  
  


  #Step 1: Generate data through sampling
  u2_samp <- mvrnorm(J, mu.u2_init, Sigma=sigma2.u2_init)
  l2_samp <- matrix(nrow=J,ncol=length(mu.u2_init)+1); colnames(l2_samp) <- c("ID",paste("u",1:length(mu.u2_init),sep='')); l2_samp <- data.frame(l2_samp)
  l2_samp[,"ID"]<-1:J; l2_samp[,-1]<-u2_samp
  
  X_samp <- rnorm(n, mu.X_init, sqrt(sigma2.X_init))
  e_samp <- rnorm(n,0, sqrt(sigma2_init))
  
  l1_samp <- matrix(nrow=n, ncol=3); colnames(l1_samp) <- c("ID", "X", "e");l1_samp <- data.frame(l1_samp)
  l1_samp[,"ID"]<-1:n; l1_samp[,"X"]<-X_samp; l1_samp[,"e"]<-e_samp
  
  l1_assign <- matrix(trunc(runif(n*length(mu.u2_init), min=1, max=J+1)),nrow=n)
  l1_l2_xref <-matrix(nrow=n, ncol=length(mu.u2_init)+1); colnames(l1_l2_xref) <- c("l1_ID",paste("l2_ID",1:length(mu.u2_init),sep='')); l1_l2_xref <- data.frame(l1_l2_xref)
  l1_l2_xref[,"l1_ID"]<-1:n; l1_l2_xref[,2]<-l1_assign[,1];
  l1_l2_xref[1:trunc(mobility*n),-c(1,2)]<-l1_assign[1:trunc(mobility*n),-1];l1_l2_xref[(trunc(mobility*n)+1):n,-c(1,2)]<-l1_assign[(trunc(mobility*n)+1):n,1]
  
  data_samp <- matrix(nrow=n,ncol=length(mu.u2_init)+2); colnames(data_samp) <- c(paste("group",1:length(mu.u2_init),sep=''),"y","X"); data_samp <- data.frame(data_samp)
  data_samp[,1:length(mu.u2_init)]<-l1_l2_xref[,-1]
  data_samp[,"X"]<-l1_samp$X
  
  data_samp[,"y"] <- beta_init[1] + l2_samp$u1[data_samp[,"group1"]] + l2_samp$u2[data_samp[,"group2"]] + l2_samp$u3[data_samp[,"group3"]] + l2_samp$u4[data_samp[,"group4"]] +
    beta_init[2]*data_samp[,"X"] + l1_samp$e
  
  return(data_samp)
}

# no time
# tm <- system.time(mydata <- UDF_sample(mobility = c(.2), J = c(100),rho = c(FALSE), tau = c("same")))


```

# Make data list

Questions: ccrem doesn't use w... so does it interfere when reading in list to stan? 

```{r}


getdata_ccrem_mmrem <- function(data){
 # pre_data
k = 4
id <- c(paste("group",1:k,sep=""))
gm = 1
predictor="X"

# data 
y <- data$y
J <- length(levels(as.factor(data[,id[1]])))
n <- dim(data)[1]

if(gm == 1)
  {
    x <- data[,predictor] - mean(data[,predictor])
  } else
  {
    x <- data[,predictor]
  }

W <- diag(k)
w <- matrix(rep(1/k,n*k),ncol=k, nrow=n)
  
for(i in 1:k) {assign(paste("group",i,sep=''),data[,id[i]])}
  
for (i in 1:n) {
  
  if (group1[i]==group2[i]){
    w[i,1]=w[i,1]+0.25
    w[i,2]=0
  } 
  
  if (group1[i]==group3[i]){
    w[i,1]=w[i,1]+0.25
    w[i,3]=0
  } 
  else 
    if (group2[i]==group3[i]){
      w[i,2]=w[i,2]+0.25
      w[i,3]=0
    } 
  
  
  if (group1[i]==group4[i]){
    w[i,1]=w[i,1]+0.25
    w[i,4]=0
  } 
  else {
    if (group2[i]==group4[i]){
      w[i,2]=w[i,2]+0.25
      w[i,4]=0
    } 
    
    else 
      if (group3[i]==group4[i]){
        w[i,3]=w[i,3]+0.25
        w[i,4]=0
      }
  }
  
}

group1 <- data$group1
group2 <- data$group2
group3 <- data$group3
group4 <- data$group4

ccrem_mmrem_data <- list(y = y, J = J, n = n, w = w, x = x, 
               group1 = group1, group2 = group2, 
               group3 = group3, group4 = group4)
  
return(ccrem_mmrem_data)

}



#system.time(listdata <- getdata_ccrem_mmrem(mydata))

getdata_rccrem <- function(data){
 #Check on this
  k = 4
  id <- c(paste("group",1:k,sep=""))
  gm = 1
  predictor="X"
  
  ####
  
  y <- data$y
  
  J <- length(levels(as.factor(data[,id[1]])))
  n <- dim(data)[1]
  
if(gm == 1)
  {
    x <- data[,predictor] - mean(data[,predictor])
  } else
  {
    x <- data[,predictor]
  }
  
W <- diag (k)

  
for(i in 1:k) {assign(paste("group",i,sep=''),data[,id[i]])}
  
group1 <- data$group1
group2 <- data$group2
group3 <- data$group3
group4 <- data$group4

zeros = rep(0, 4)

rccrem_data <- list(y=y, J=J, n=n, group1=group1, group2=group2, group3=group3, group4=group4, x= x, W=W, zeros = zeros) 
  
return(rccrem_data)

}
```

sets iterations, cores, thin_val the same... may want to add separate values for rccrem and mmrem/ccrem.


Need to modify return dataframe. 

Add in 50% 

add in Na column to make it match

loo and waic

```{r}
run_mmrem <-
  function(data,
           iterations = 10000,
           warmup_val = 5000,
           thin_val = 10,
           chains_val = 4,
           cores_val = 4,
           adapt_delta = 0.999,
           max_treedepth = 25) {
    
    

  suppressPackageStartupMessages(require(rstan))
    
  suppressPackageStartupMessages(require(loo))
    
    

    
    
    ccrem_mmrem_data <- getdata_ccrem_mmrem(data)
    
        
  # system.time( 
    
    mm_stan_fit <-
      stan(
        model_code = mmrem_model,
        data = ccrem_mmrem_data,
        iter = iterations,
        warmup = warmup_val,
        thin = thin_val,
        chains = chains_val,
        cores = cores_val, ### change this maybe
        control = list(adapt_delta = adapt_delta, max_treedepth = max_treedepth)
      )
 #  )
    
    # LOO 
    mm_loo <- loo(mm_stan_fit, k_threshold = 0.7, save_psis = TRUE)

    
    LL_mm <- extract_log_lik(mm_stan_fit) # matrix
    mm_waic <- waic(LL_mm)
    
      return(
    data.frame(
      model = "mmrem",
                    int_mean = summary(mm_stan_fit)$summary["popint", "mean"],
                    int_median = summary(mm_stan_fit)$summary["popint", "50%"],#median instead? 50%
                    slope_mean = summary(mm_stan_fit)$summary["popslope", "mean"],
                    slope_median = summary(mm_stan_fit)$summary["popslope", "50%"],
                    sigma_y_mean = summary(mm_stan_fit)$summary["sigma_y", "mean"],
                    sigma_y_median = summary(mm_stan_fit)$summary["sigma_y", "50%"],
                    sigma_u2_mean = summary(mm_stan_fit)$summary["sigma_u2", "mean"],
                    sigma_u2_median = summary(mm_stan_fit)$summary["sigma_u2", "50%"],
                    loo_est = mm_loo$estimates["looic", "Estimate"],
                    waic_est = mm_waic$estimates["waic", "Estimate"]
            
      )
  )
    
    
  }


#system.time(test <- run_mmrem(data= mydata))


run_ccrem <-
  function(data,
          iterations =  25000,
           warmup_val = 15000,
           thin_val = 10,
           chains_val = 2,
           cores_val = 4,
           adapt_delta = 0.999,
           max_treedepth = 25) {
    
      suppressPackageStartupMessages(require(rstan))
    
  suppressPackageStartupMessages(require(loo))
    
    ccrem_mmrem_data <- getdata_ccrem_mmrem(data)
    
        
  # system.time( 
    cc_stan_fit <-
      stan(
        model_code = ccrem_model,
        data = ccrem_mmrem_data,
        iter = iterations,
        warmup = warmup_val,
        thin = thin_val,
        chains = chains_val,
        cores = cores_val,
        control = list(adapt_delta = adapt_delta, max_treedepth = max_treedepth)
      )
#    )
    
        # LOO 
    cc_loo <- loo(cc_stan_fit, k_threshold = 0.7, save_psis = TRUE)
    
    
    LL_cc <- extract_log_lik(cc_stan_fit)
    cc_waic <- waic(LL_cc)
    
    
    return(data.frame(model = "mmrem",
                    int_mean = summary(cc_stan_fit)$summary["popint", "mean"],
                    int_median = summary(cc_stan_fit)$summary["popint", "50%"],
                    slope_mean = summary(cc_stan_fit)$summary["popslope", "mean"],
                    slope_median = summary(cc_stan_fit)$summary["popslope", "50%"],
                    sigma_y_mean = summary(cc_stan_fit)$summary["sigma_y", "mean"],
                    sigma_y_median = summary(cc_stan_fit)$summary["sigma_y", "50%"],
                    sigma_u2_1_mean = summary(cc_stan_fit)$summary["sigma_u2[1]", "mean"],
                    sigma_u2_1_median = summary(cc_stan_fit)$summary["sigma_u2[1]", "50%"],
                    sigma_u2_2_mean =  summary(cc_stan_fit)$summary["sigma_u2[2]", "mean"],
                    sigma_u2_2_median =  summary(cc_stan_fit)$summary["sigma_u2[2]", "50%"],
                    sigma_u2_3_mean = summary(cc_stan_fit)$summary["sigma_u2[3]", "mean"],
                    sigma_u2_3_median = summary(cc_stan_fit)$summary["sigma_u2[3]", "50%"],
                    sigma_u2_4_mean =  summary(cc_stan_fit)$summary["sigma_u2[4]", "mean"],
                    sigma_u2_4_median =  summary(cc_stan_fit)$summary["sigma_u2[4]", "50%"],
                    loo_est = cc_loo$estimates["looic", "Estimate"],
                    waic_est = cc_waic$estimates["waic", "Estimate"] )
                      )
                      
                      
  }

#system.time(test2 <- run_ccrem(data= mydata))


run_rccrem <-
  function(data,
           iterations =  50000,
           warmup_val = 25000,
           thin_val = 10,
           chains_val = 2,
           cores_val = 4,
           adapt_delta = 0.999,
           max_treedepth = 25) {
    
    
      suppressPackageStartupMessages(require(rstan))
    
  suppressPackageStartupMessages(require(loo))
    
    rccrem_data <- getdata_rccrem(data)
  
    
  # system.time( 
     rcc_stan_fit <-
      stan(
        model_code = rccrem_model_new,
        data = rccrem_data,
        iter = iterations,
        warmup = warmup_val,
        thin = thin_val,
        chains = chains_val,
        cores = cores_val,
        control = list(adapt_delta = adapt_delta, max_treedepth = max_treedepth)
      )
  #   )
    
    
          # LOO 
    rcc_loo <- loo(rcc_stan_fit, k_threshold = 0.7, save_psis = TRUE)
    
    LL_rcc <- extract_log_lik(rcc_stan_fit)
    rcc_waic <- waic(LL_rcc)
    
    
    return(data.frame(model = "mmrem",                    
               int_mean = summary(rcc_stan_fit)$summary["popint", "mean"],
               int_median = summary(rcc_stan_fit)$summary["popint", "50%"],
               slope_mean = summary(rcc_stan_fit)$summary["popslope", "mean"],
               slope_median =  summary(rcc_stan_fit)$summary["popslope", "50%"],
               sigma_y_mean = summary(rcc_stan_fit)$summary["sigma_y", "mean"],
               sigma_y_median = summary(rcc_stan_fit)$summary["sigma_y", "50%"],
               sigma_u2_1_mean = summary(rcc_stan_fit)$summary["sigma_u2[1]", "mean"],
               sigma_u2_1_median =  summary(rcc_stan_fit)$summary["sigma_u2[1]", "50%"],
               sigma_u2_2_mean =  summary(rcc_stan_fit)$summary["sigma_u2[2]", "mean"],
               sigma_u2_2_median = summary(rcc_stan_fit)$summary["sigma_u2[2]", "50%"],
               sigma_u2_3_mean = summary(rcc_stan_fit)$summary["sigma_u2[3]", "mean"],
               sigma_u2_3_median = summary(rcc_stan_fit)$summary["sigma_u2[3]", "50%"],
               sigma_u2_4_mean =  summary(rcc_stan_fit)$summary["sigma_u2[4]", "mean"],
               sigma_u2_4_median = summary(rcc_stan_fit)$summary["sigma_u2[4]", "50%"],
               rho_12_mean = summary(rcc_stan_fit)$summary["rho_12", "mean"],
               rho_12_median = summary(rcc_stan_fit)$summary["rho_12", "50%"],
               rho_13_mean = summary(rcc_stan_fit)$summary["rho_13", "mean"],
               rho_13_median = summary(rcc_stan_fit)$summary["rho_13", "50%"],
               rho_14_mean = summary(rcc_stan_fit)$summary["rho_14", "mean"],
               rho_14_median = summary(rcc_stan_fit)$summary["rho_14", "50%"],
               rho_23_mean =  summary(rcc_stan_fit)$summary["rho_23", "mean"],
               rho_23_median = summary(rcc_stan_fit)$summary["rho_23", "50%"],
               rho_24_mean = summary(rcc_stan_fit)$summary["rho_24", "mean"],
               rho_24_median = summary(rcc_stan_fit)$summary["rho_24", "50%"],
               rho_34_mean =  summary(rcc_stan_fit)$summary["rho_34", "mean"],
               rho_34_median = summary(rcc_stan_fit)$summary["rho_34", "50%"],
               loo_est = rcc_loo$estimates["looic", "Estimate"],
               waic_est = rcc_waic$estimates["waic", "Estimate"]
                      
                      ))
                      
                      
  }



system.time(test3 <- run_rccrem(data= mydata))

```




```{r}

runmodels <- function(data, mmrem=TRUE, ccrem=TRUE, rccrem=TRUE){
  suppressPackageStartupMessages(require(dplyr))
  
  res <- data.frame()


    if (mmrem) {
      res_mmrem <- run_mmrem(data)
      
      res <- bind_rows(list(res, res_mmrem))
      
    }
  
      if (ccrem) {
      res_ccrem <- run_ccrem(data)
      
      res <- bind_rows(list(res, res_ccrem))
      
      }
  
      if (rccrem) {
      res_rccrem <- run_rccrem(data)
      
      res <- bind_rows(list(res, res_rccrem))

      
    }
    
  res


  
}


res <- runmodels(data= mydata)

```



```{r}


runSim <- function(reps, mobility, J, rho, tau, mmrem=TRUE, ccrem=TRUE, rccrem=TRUE, seed = NULL, ...){
  
   suppressPackageStartupMessages(require(purrr))
  suppressPackageStartupMessages(require(dplyr))
  
  if (!is.null(seed)) set.seed(seed)
  
    replicates <- rerun(reps, {
    UDF_sample(mobility = mobility, J = J, rho=rho, tau=tau) %>%
      runmodels(mmrem = mmrem,ccrem = ccrem, rccrem= rccrem)
  })
  
    
    #fix this... 
  replicates %>%
    bind_rows() %>%
    group_by(model) #%>% 
 summarise(K = n(),
          variance = var(popint),
          
          
        #  rel_bias_icc = (mean(popint) - int)/(int),
        #  rel_bias_icc_mcse = sqrt(variance/(K*(int^2)))
    
    )
  
}

# 95% CI relative bias

# 


#CXX14 = "C:/Rtools/mingw_64/bin/g++.exe"


#runSim(reps=2, mobility = c(.2), J = c(100),rho = c(FALSE), tau = c("same"))
```


Need to rework this...might need to redo UDF_sample. reads in whole variance/covariance matrix for condition.. maybe save as strings that are then made into matrices as solution??

```{r, eval= F}
library(dplyr)
library(purrr)
library(Pusto)


set.seed(778321311)
# Experimental factors
mobility <- c(.2,.1)
J <- c(100, 50)
rho <- c(FALSE, TRUE)
tau <- c("same", "different" )



# #probably won't work.. need to figure out. 
# sigma2.u2_init <-
#   c("10,0,0,0, 0,10 "
#     rbind(c(10, 0, 0, 0), c(0, 10, 0, 0), c(0, 0, 10, 0), c(0, 0, 0, 10)), #1
#     rbind(c(10, 0, 0, 0), c(0, 12, 0, 0), c(0, 0, 14, 0), c(0, 0, 0, 16)), #2
#     rbind(c(10, 6, 5, 4), c(6, 10, 6, 5), c(5, 6, 10, 6), c(4, 5, 6, 10)), #3
#     rbind(c(10, 6.57, 5.92, 5.06), c(6.57, 12, 7.78, 6.93), c(5.92, 7.78, 14, 8.98),c(5.06, 6.93, 8.98, 16))
#     )




#not conditions.. maybe set as default. 

# Number of replications
reps <- 2


param_list <- list(
  mobility=mobility, 
  J=J, 
  rho = rho, 
  tau = tau,
  reps = reps
)


#not_right..
params <- 
  param_list %>%
  cross_df() %>%
  mutate(
    seed = 1:n() + sample(2^30, size = 1),
  )

rownames(params) <- NULL

print(paste0(nrow(params), " fully crossed experimental conditions have been generated."))



source_obj <- setdiff(ls(), c("params"))


```



```{r, eval= F}

library(Pusto)

cluster <- Pusto::start_parallel(source_obj = source_obj, setup = "register")

tm <- system.time(
  results <- plyr::mdply(params, .f = runSim, 
                         .parallel = TRUE)
)

tm 
parallel::stopCluster(cluster)

session_info <- sessionInfo()
run_date <- date()

save(params, results, session_info, run_date, file = "Simulations/simulation results.Rdata")



```

